systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2005-11-07 paper/trunk/systemfit_other.tex
a consistent BibTeX key pattern is now used throughout the whole article: [lastname of first author][last two digits of year]
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@583 591db2bd-e0a0-4d22-8c19-2192dbb7da31

Hausman \citep{hausman1978} developed a test have power against
alternatives for which $\hat{\theta}$ and $\tilde{\theta}$ diverge
under misspecification.
The resulting test statistic, distributed as a
$\chi^2$, is the difference between the covariance of an
efficient and the covariance of the inefficient estimator is zero, if the
model is correctly specified.

@@

As linear systems of equations can be estimated using
\code{systemfit}, nonlinear systems of equations \citep{hausman-1975}
can be estimated using a similar function \code{nlsystemfit}.
The usage for the nonlinear estimation function is similar to
\code{systemfit} and can estimate system of equations using OLS, SUR,
2SLS and 3SLS methods.

>>>>

Hausman \citep{hausman78} developed a test have power against
alternatives for which $\hat{\theta}$ and $\tilde{\theta}$ diverge
under misspecification.
The resulting test statistic, distributed as a
$\chi^2$, is the difference between the covariance of an
efficient and the covariance of the inefficient estimator is zero, if the
model is correctly specified.

@@

As linear systems of equations can be estimated using
\code{systemfit}, nonlinear systems of equations \citep{hausman75}
can be estimated using a similar function \code{nlsystemfit}.
The usage for the nonlinear estimation function is similar to
\code{systemfit} and can estimate system of equations using OLS, SUR,
2SLS and 3SLS methods.
